How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-17 docs/PhysicsPaper/StokesErosion.tex
N
NM

Flow-induced erosion acts across a range of scales in the natural world, from massive geological structures sculpted by wind or water \cite{abrams2009growth, perkins2015amplification, mac2020ultra, sharma2022alcove, mac2022morphological}, to mesoscopic patterns formed by surface or internal flows \cite{berhanu2012shape, bertagni2021hydrodynamic}, and down to the granular constituents of porous media as they slowly disintegrate in groundwater flows \cite{zareei2022temporal}. The shape-flow feedback of erosion can imprint across all of these scales, affecting both large-scale features and small-scale ones, such as the microstructure of porous materials.
The porous media encountered in nature, for example, typically exhibit material {\em anisotropy} in that they permit seepage flow in certain directions more easily than in others. Typical materials are more permeable to flow in the longitudinal (or horizontal) direction than transversely by a factor of 5-20 \cite{bear1988dynamics, anderson2015applied}. Most commonly, this material anisotropy is attributed to the sedimentation process, in which, due to the fluid-structure interaction, non-spherical particles tend to settle with their long axis parallel to the plan of deposition \cite{bear1988dynamics}. Controlled experiments, however, have not been performed to test this hypothesis, and other mechanisms may be at work. Here, we use highly-accurate numerical simulations to examine an alternative, and possibly complementary, mechanism: namely, that the flow-induced erosion of the medium's solid constituents contributes to its overall anisotropy.

Our method merges highly-efficient and highly-accurate boundary-integral equation (BIE) methods with stable interface evolution methods to simulate the erosion of dense suspensions of solid bodies in the Stokes regime of groundwater flow \cite{quaife2018boundary}. Originally inspired by related work in the high-Reynolds-number regime \cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017}, our method is documented, validated, benchmarked in \cite{quaife2018boundary}, and can simulate the erosion of $O(100)$ solid bodies. The more recent Cauchy reformulation of the BIE and the associated  quadrature formulas allow us to resolve points of near contact between bodies, thus enabling high-fidelity simulation of dense suspensions of erodable bodies \cite{chiu2020viscous}.

@@

%-----------------------------------------------------------------------------------------------%
\section{Measuring permeability and other porous-media properties}
\label{sec:}
%-----------------------------------------------------------------------------------------------%

@@

>>>>

Flow-induced erosion acts across a range of scales in the natural world, from massive geological structures sculpted by wind or water \cite{abrams2009growth, perkins2015amplification, mac2020ultra, sharma2022alcove, mac2022morphological}, to mesoscopic patterns formed by surface or internal flows \cite{berhanu2012shape, bertagni2021hydrodynamic}, and down to the granular constituents of porous media as they slowly disintegrate in groundwater flows \cite{zareei2022temporal}. The associated nonlinear feedback between changing shapes and the surrounding flows can imprint across all of these scales, affecting both large-scale features and small-scale ones, such as the microstructure of porous materials.
The porous media encountered in nature, for example, typically exhibit material {\em anisotropy} in that they permit seepage flow in certain directions more easily than in others. Typical materials are more permeable to flow in the longitudinal (or horizontal) direction than transversely by a factor of 5-20 \cite{bear1988dynamics, anderson2015applied}. Most commonly, this material anisotropy is attributed to the sedimentation process, in which, due to the fluid-structure interaction, non-spherical particles tend to settle with their long axis parallel to the plan of deposition \cite{bear1988dynamics}. Controlled experiments, however, have not been performed to test this hypothesis, and other mechanisms may be at work. Here, we use highly-accurate numerical simulations to examine an alternative, and possibly complementary, mechanism: namely, that the flow-induced erosion of the medium's solid constituents contributes to its overall anisotropy.

Our method merges highly-efficient and highly-accurate boundary-integral equation (BIE) methods with stable interface evolution methods to simulate the erosion of dense suspensions of solid bodies in the Stokes regime of groundwater flow \cite{quaife2018boundary}. Originally inspired by related work in the high-Reynolds-number regime \cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017}, our method is documented, validated, benchmarked in \cite{quaife2018boundary}, and can simulate the erosion of $O(100)$ solid bodies. The more recent Cauchy reformulation of the BIE and the associated  quadrature formulas allow us to resolve points of near contact between bodies, thus enabling high-fidelity simulation of dense suspensions of erodable bodies \cite{chiu2020viscous}. Though the governing fluid-flow equations (Stokes) in this regime are linear, the feedback between complex eroding geometries and the flow leads to highly nonlinear behavior.

@@

%-----------------------------------------------------------------------------------------------%
\section{Measuring porous-media properties: permeability, drag, and anisotropy}
\label{sec:}
%-----------------------------------------------------------------------------------------------%

@@

%-----------------------------------------------------------------------------------------------%
\section{Results}
%-----------------------------------------------------------------------------------------------%

We now do stuff
